Describing the C-space of asynchronous periodic task using DIT

### 2013-07-22 dit-paper_ieee.tex
Completed Section on Asynchronous DIT

  We consider systems of periodic concrete tasks with constrained deadline on uniprocessor platform, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period. The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In the following, we differentiate between \emph{synchronous systems} (where $O_i = 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

@@

  Furthermore, the following notations are used:
  \begin{itemize}
    \item $\tau = (\tau_0, \cdots, \tau_{n-1})$
    \item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
    \item $O_{max} = \max (O_0, \cdots, O_{n-1})$
    \item idle time...
    \item busy period...
  \end{itemize}

@@

\begin{definition}
A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.\\
\end{definition}

@@

  In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT, along with an algorithm to find its value and an EDF feasibility condition based on it. In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[O_{max}, O_{max} + 2 H]$ is sufficient to consider.

@@

This system is guaranteed to have at least one solution modulo $H$ if the following condition is respected $$a_i + O_i \equiv a_j + O_j \; (mod \; \operatorname{gcd}(T_i, T_j))$$

@@

\bibliographystyle{latex8}
\bibliography{dit-paper}

>>>>

  We consider a discrete time and systems of periodic concrete tasks with constrained deadline on uniprocessor platform, where each task $\tau_i$ is represented by a tuple $(O_i, C_i, D_i, T_i)$ where $O_i$ is the offset value, $C_i$ the execution time, $D_i$ the relative deadline and $T_i$ the period. The constrained deadline property implies that $D_i \leq T_i \; \forall i$. In the following, we differentiate between \emph{synchronous systems} (where $O_i = 0 \; \forall i$) and \emph{asynchronous systems} (which are not synchronous).\\

@@

  Furthermore, the following notations are used:
  \begin{itemize}
    \item $\tau = (\tau_0, \cdots, \tau_{n-1})$
    \item $H = \operatorname{lcm}(T_0, \cdots, t_{n-1})$
    \item $O_{max} = \max (O_0, \cdots, O_{n-1})$
    \item An \emph{idle time} is an instant $t$ at which each job that arrived strictly before $t$ has finished its execution.
    \item The interval between the initial time and the first idle time is called the \emph{busy period}.
  \end{itemize}

@@

\begin{definition}
A \textbf{definitive idle time} (DIT) is a time $t$ such that every job released strictly before instant $t$ has its absolute deadline before or at instant $t$.
\end{definition}

\begin{definition}
The earliest DIT occurring in the system strictly after $t=0$ is called the \textbf{first DIT} and is noted $t_d$.
\end{definition}

The value of the first DIT can be found by solving the following equation:
\[
  t_d = \min \left( t \; s.t. \; \forall i:
  \left\{
  \begin{array}{c}
    t \equiv a_i \; (mod \; T_i) \\
    a_i \in [D_i, T_i]
  \end{array}
  \right.
  \right)
\]

\begin{remark} (from the definition):
 \begin{itemize}
  \item Contrary to the idle times, the DITs are independent of the scheduling or the execution times of the jobs.
  \item In feasible system, every DIT is an idle time.
  \item In feasible system, the first DIT happens after the end of the busy period.
  \item As $H$ is always a DIT, we have $t_d \leq H$.
 \end{itemize}
\end{remark}

Every DIT being an idle instant, the execution of the system after it does not depend on what happened previously. Because the synchronous arrival pattern is the worst case [citation needed], it is sufficient for the DBF test to only consider intervals $[0, t]$ with $t$ being a deadline before the first DIT.\\

To summarize, we reduced the description of the C-space from an infinite number of equations to only the equations where $t_1 = 0$, $t_2 \leq t_d$ and $t_2$ correspond to a deadline job. Note that this is still exponential in the number of tasks.

@@

  In this paper, we extend the work of \cite{george2009characterization} to the asynchronous case. In section \ref{sct:asyncDIT}, we present an extension of the concept of DIT adapted to the asynchronous case called first periodic DIT ($t_d$), along with an algorithm to find its value. In Section \ref{sct:asyncCspace}, we show how to describe the C-space of an asynchronous system based on the DBF test, and we show why the interval $[t_d, t_d + H]$ is sufficient to consider.

@@

This system is guaranteed to have at least one solution modulo $H$ for given values of $a_i$ if the following condition is respected $$a_i + O_i \equiv a_j + O_j \; (\operatorname{mod} \; \operatorname{gcd}(T_i, T_j)) \; \forall i, j$$

@@

\nocite{*}
\bibliographystyle{latex8}
\bibliography{dit-paper}
